---
title: "Statistic Model to Analyze Student’s Performance - Group 8"
author: "Xuchuan Zheng, Sungki Park, Prashant Sharma"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: default
  html_document: default
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```


```{r eval=TRUE, echo=FALSE}
# Library
library(olsrr)
```

# 1. _Introduction_

In out final project for Data 603 - Statistical Modelling with Data, we have tried to develop a model to analyze the impact of various demographic and social factors on the performance of students. Academic performance, though it is not the only factor but is one of the crucial factors in shaping a student's future. To get into a good collage/university, student must score grades in school, a good college ca lead a better future and economic stability. So in order to secure good grades, getting into a great school is enough? Is there something more than a great school that can help a student to perform better? Do the social and demographic factors plays any role in student's performance? In our project we are trying to answer these question.

To answer these questions we are working with a dataset that is collected at 2 Portuguese schools for Mathematics and Portuguese subject. This data is collected by using school reports and questionnaires. The data attribute include students grades, family size information, education level of parents, free time of student, any many other factors. By working on this project we are hoping to develop more understanding about the factors which can impact the performance of a student.

$$
\\
$$

# 2. _Data_

This data is from [UC Irvine Machine Learning Repository](https://archive.ics.uci.edu/dataset/320/student+performance). There are 649 rows instances and 30 features in the dataset. Below are details of each feature

1. school - student's school (binary: 'GP' - Gabriel Pereira or 'MS' - Mousinho da Silveira) [Qualitative]

2. sex - student's sex (binary: 'F' - female or 'M' - male) [Qualitative]

3. age - student's age (numeric: from 15 to 22)

4. address - student's home address type (binary: 'U' - urban or 'R' - rural) [Qualitative]

5. famsize - family size (binary: 'LE3' - less or equal to 3 or 'GT3' - greater than 3) [Qualitative]

6. Pstatus - parent's cohabitation status (binary: 'T' - living together or 'A' - apart) [Qualitative]

7. Medu - mother's education (numeric: 0 - none,  1 - primary education (4th grade), 2 - 5th to 9th grade, 3 - secondary education or 4 - higher education) [Qualitative]

8. Fedu - father's education (numeric: 0 - none,  1 - primary education (4th grade), 2 - 5th to 9th grade, 3 - secondary education or 4 -  higher education) [Qualitative]

9. Mjob - mother's job (nominal: 'teacher', 'health' care related, civil 'services' (e.g. administrative or police), 'at_home' or 'other') [Qualitative]

10. Fjob - father's job (nominal: 'teacher', 'health' care related, civil 'services' (e.g. administrative or police), 'at_home' or 'other') [Qualitative]

11. reason - reason to choose this school (nominal: close to 'home', school 'reputation', 'course' preference or 'other') [Qualitative]

12. guardian - student's guardian (nominal: 'mother', 'father' or 'other') [Qualitative]

13. traveltime - home to school travel time (numeric: 1 - <15 min., 2 - 15 to 30 min., 3 - 30 min. to 1 hour, or 4 - >1 hour) [Qualitative]

14. studytime - weekly study time (numeric: 1 - <2 hours, 2 - 2 to 5 hours, 3 - 5 to 10 hours, or 4 - >10 hours) [Qualitative]

15. failures - number of past class failures (numeric: n if 1<=n<3, else 4) [Qualitative]

16. schoolsup - extra educational support (binary: yes or no) [Qualitative]

17. famsup - family educational support (binary: yes or no) [Qualitative]

18. paid - extra paid classes within the course subject (Math or Portuguese) (binary: yes or no) [Qualitative]

19. activities - extra-curricular activities (binary: yes or no) [Qualitative]

20. nursery - attended nursery school (binary: yes or no) [Qualitative]

21. higher - wants to take higher education (binary: yes or no) [Qualitative]

22. internet - Internet access at home (binary: yes or no) [Qualitative]

23. romantic - with a romantic relationship (binary: yes or no) [Qualitative]

24. famrel - quality of family relationships (numeric: from 1 - very bad to 5 - excellent) [Qualitative]

25. freetime - free time after school (numeric: from 1 - very low to 5 - very high) [Qualitative]

26. goout - going out with friends (numeric: from 1 - very low to 5 - very high) [Qualitative]

27. Dalc - workday alcohol consumption (numeric: from 1 - very low to 5 - very high) [Qualitative]

28. Walc - weekend alcohol consumption (numeric: from 1 - very low to 5 - very high) [Qualitative]

29. health - current health status (numeric: from 1 - very bad to 5 - very good) [Qualitative]

30. absences - number of school absences (numeric: from 0 to 93) [Quantitative]

31. G1 - first period grade (numeric: from 0 to 20) [Quantitative]

32. G2 - second period grade (numeric: from 0 to 20) [Quantitative]

33. G3 - final grade (numeric: from 0 to 20, output target) [Quantitative]


**G3 (Final grade) is the dependent variable for our model.**

>NOTE: We need to convert the qualitative variable from numeric to string

$$
\\
$$



```{r eval=TRUE, echo=FALSE}
studentDataset_por = read.csv("https://raw.githubusercontent.com/prs-sharma9/DATA-603_PROJECT/main/dataset/student-por.csv", sep = ";")
studentDataset_mat = read.csv("https://raw.githubusercontent.com/prs-sharma9/DATA-603_PROJECT/main/dataset/student-mat.csv", sep = ";")


```

```{r}
studentDataset_por[which(studentDataset_por$Medu==1),7] = "one"
studentDataset_por[which(studentDataset_por$traveltime==1),13] = "one"
studentDataset_por[which(studentDataset_por$Fedu==1),8] = "one"
studentDataset_por[which(studentDataset_por$studytime==1),14] = "one"
studentDataset_por[which(studentDataset_por$famrel==1),24] = "one"
studentDataset_por[which(studentDataset_por$freetime==1),25] = "one"
studentDataset_por[which(studentDataset_por$goout==1),26] = "one"
studentDataset_por[which(studentDataset_por$Walc==1),28] = "one"
studentDataset_por[which(studentDataset_por$Dalc==1),27] = "one"
studentDataset_por[which(studentDataset_por$health==1),29] = "one"

studentDataset_mat[which(studentDataset_por$Medu==1),7] = "one"
studentDataset_mat[which(studentDataset_por$traveltime==1),13] = "one"
studentDataset_mat[which(studentDataset_por$Fedu==1),8] = "one"
studentDataset_mat[which(studentDataset_por$studytime==1),14] = "one"
studentDataset_mat[which(studentDataset_por$famrel==1),24] = "one"
studentDataset_mat[which(studentDataset_por$freetime==1),25] = "one"
studentDataset_mat[which(studentDataset_por$goout==1),26] = "one"
studentDataset_mat[which(studentDataset_por$Walc==1),28] = "one"
studentDataset_mat[which(studentDataset_por$Dalc==1),27] = "one"
studentDataset_mat[which(studentDataset_por$health==1),29] = "one"

# Combining Math and Por data set to create one dataframe

studentDataset = rbind(studentDataset_por, studentDataset_mat)
head(studentDataset, 3)
```



# _Methodology_

Below is the outline of the steps we are going to perform in our analysis:

1. First Build a full additive model.

2. We will apply some model selection technique to come up with the best additive model.

2. Based on p-value (assuming $\alpha = 0.05$) we will drop variable which are non-significant.

3. Perform partial F-test to verify that dropped variables are indeed non-significant.

4. Provide interpretation for the best additive model to predict our dependent variable (G3 - Final Grades).

5. Based on our best additive model, we will check for interaction between the variables.

6. Using p-value (assuming $\alpha = 0.05$), we will drop the non-significant interaction terms.

7. Use partial F-test and analysis of Variance to verify the usability of our best interaction model.

8. Provide interpretation of our best interaction model.

9. Then we will check if we can include any higher order term in our model (Moving towards Higher order multiple regression model).

10. Verify the significance of higher order terms using p-value (assuming $\alpha = 0.05$).

11. Once we have done all our analysis we will try to define our best regression model (liner or higher order) to predict our dependent variable (G3 - Final Grades).

12. Using our final regression model, we will start checking the regression assumptions.

13. Linearity Assumption.

14. Independence Assumption.

15. Normality Assumption.

16. Multi-collinearity.

17. Outliers.

$$
\\
$$


```{r eval=TRUE, echo=FALSE}
# Reading data from github
# studentDataset = read.csv("https://raw.githubusercontent.com/prs-sharma9/DATA-603_PROJECT/main/dataset/student-por.csv", sep = ";")
# head(studentDataset, 3)
```

Starting our analysis with building additive model, then we will try to include interaction terms and higher order terms in our model.

## 3.1 _Full Additive Model_

Creating full additive model: 

```{r}
studentPerformance_fm = lm(G3 ~(school+sex+age+address+famsize+Pstatus+Medu+
                                  Fedu+Mjob+Fjob+reason+guardian+traveltime+studytime+
                                  failures+schoolsup+famsup+activities+nursery+higher+internet+
                                  romantic+famrel+freetime+
                                  goout+Dalc+Walc+health+absences), 
                           data = studentDataset)

summary(studentPerformance_fm)
```
$$
\\
$$

From the summary of the full model we can see that many of the variables are non-significant. We can apply some techniques for model selection to get significant parameters.


## 3.2 _Model Selection_

Using Stepwise model selection procedure to get the significant parameters:

```{r}
studentPerformance_stepwise=ols_step_both_p(studentPerformance_fm,p_enter = 0.1, p_remove = 0.3, details=FALSE)
summary(studentPerformance_stepwise$model)
```


Getting best subset

```{r}
#ExecSubsets=ols_step_best_subset(studentPerformance_fm, details=TRUE)
#ExecSubsets$metrics
```


# Appendix


***

$$
END
$$




```{r}
studentPerformance_p1 = lm(G3 ~ (sex+age+address+famsize+Pstatus+Medu+Fedu+traveltime+studytime+
                                   failures+schoolsup+famsup+activities+higher+internet+romantic+
                                   famrel+freetime+goout+Dalc+Walc+health+absences), 
                           data = studentDataset)

summary(studentPerformance_p1)
```


```{r}
subsets = ols_step_forward_p(studentPerformance_fm,p_val = 0.05, details = FALSE)
forwardMdl = subsets$model
summary(forwardMdl)
```

```{r}
bestSubsetMdl = ols_step_best_subset(forwardMdl, details = FALSE)
(bestSubsetMdl$metrics)
```

```{r}
forwardMdl_int = lm(G3 ~ (failures+higher+schoolsup+studytime+romantic+goout+health+Mjob)^2, data = studentDataset)
summary(forwardMdl_int)
```


```{r}
forwardMdl_int1 = lm(G3 ~ (failures+higher+schoolsup+studytime+romantic+goout+health+Mjob+failures:Mjob+higher:Mjob+goout:Mjob), data = studentDataset)
summary(forwardMdl_int1)
```

```{r}
#Linearity Assumption
library(ggplot2)
ggplot(forwardMdl_int1, aes(x=.fitted, y=.resid)) +
geom_point() +geom_smooth()+
geom_hline(yintercept = 0)
```

```{r}
# Equal Variance Assumption

ggplot(forwardMdl_int1, aes(x=.fitted, y=.resid)) +
geom_point(colour = "purple") +
geom_hline(yintercept = 0) +
geom_smooth(colour = "green4")+
ggtitle("Residual plot: Residual vs Fitted values")
```

```{r}
ggplot(forwardMdl_int1, aes(x=.fitted, y=sqrt(abs(.stdresid)))) +
geom_point(colour = "purple") +
geom_hline(yintercept = 0) +
geom_smooth( colour = "green4")+
ggtitle("Scale-Location plot : Standardized Residual vs Fitted values")
```
```{r}
library(lmtest)

bptest(forwardMdl_int1)  # It doesn't have heteroscedasticity.
```

```{r}
# Normality Assumption

ggplot(data=studentDataset, aes(residuals(forwardMdl_int1))) +
geom_histogram(breaks = seq(-1,1,by=0.1), col="green3", fill="green4") +
labs(title="Histogram for residuals") +
labs(x="residuals", y="Count")
```
```{r}
ggplot(studentDataset, aes(sample=forwardMdl_int1$residuals)) +
stat_qq() +
stat_qq_line()
```
```{r}
#Testing for Normality  
shapiro.test(residuals(forwardMdl_int1))  # We don't have normality
```

```{r}
#Multicollinearity
library(mctest)
pairs(~G3+studytime+goout+health,data=studentDataset)
```


```{r}

imcdiag(forwardMdl_int1, method="VIF")
```

```{r}
forwardMdl_int2 = lm(G3 ~ (failures+higher+schoolsup+studytime+romantic+goout+health+Mjob+failures:Mjob), data = studentDataset)
summary(forwardMdl_int2)
imcdiag(forwardMdl_int2, method="VIF")
```

```{r}
# Outlier

plot(forwardMdl_int2,which=5)
```
```{r}
studentDataset[cooks.distance(forwardMdl_int2)>0.5,]
```

```{r}
plot(forwardMdl_int2,pch=18,col="red",which=c(4))
```

